A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

We would like to express our heartfelt gratitude to you and the reviewers for the insightful and helpful comments. When we revised the paper, we carefully considered and followed all the comments and suggestions provided by you and the reviewers. To summarize, we have made the following revisions:

(1) We have added the advantages \& limitations of the proposed method after experimental analysis and the future work to the conclusion.

(2) We have carefully considered and followed all the comments and suggestions related to the clarity of the writing, and made the new material a thoroughly revised manuscript.

% 消融实验
(3) We have added a new experiment to attack in the YCbCr color space to reduce the perceptibility of the pereturbations.

% % 消融实验
% (4) We have used a new way to generate the fake trajectory.

% 消融实验：噪声攻击。
(4) We have added a new experiment to evaluate the attack performance of random gaussian noise.

% 消融实验
(5) We have added a new experiment to evaluate the attack performance when only adding the perturbation to the search/template branch.

% 引用论文
(6) We have added 3 papers published in the IEEE Transactions on Circuits and Systems for Video Technology, which are most closely related to our manuscript, and analysed what is distinctive / new about our current manuscript related to these previously published papers.

@@

\textbf{For your convenience of cross checking, the new added text is shown as follows:}

\uline{
$A_{paste}$ means that, in the region where the perturbation is pasted, the pixel values of the original image is replaced with the pixel values of the perturbation.
% 解释加法
The operator $A_{add}$ means to apply additive noise, where the injecting small perturbations into the input samples. Often need constraint. the injected noise are small and sometimes invisible.  
}

%%%% 问题 2.2 %%%%
\textit{2. I agree with reviewer 3, the ground truth boxes are inaccessible to trackers during the inference. It seems that the authors use the ground truth boxes to generate the fake trajectory in lines 51-57 on page 7. Please clarify it.}

\textbf{
Thanks for the good comment. As suggest, we consider an alternative way to generate the \textit{fake trajectory} without the use of the ground truth boxes. Specifically, the attacker forces the tracker to follow a fixed direction. We illustrate this with 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
The detailed analysis of new added experiment is added in Section IV.D of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

@@

\uline{
% 介绍轨迹生成方式
\textit{Ablation Study: An alternative way to generate the fake trajectory}  Here, we consider an alternative way to generate the \textit{fake trajectory}. Specifically, the attacker forces the tracker to follow a fixed direction. We illustrate this with 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
% 分析实验结果。简单分析即可。
As shown in Table \ref{table:direction}, our attack algorithm achieves effective attacks under two different fake trajectories. Specifically, when the fake trajectory follows a fixed direction, the AO of the untargeted attack is 0.175, and the AO of the targeted attack is 0.845.
}

\begin{table}[t]
  \centering
  \caption{Influence of different ways to generate the fake trajectory. One way is the fake trajectory to follow a fixed direction. The other way is the fake trajectory to follow the real target. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Type of the Fake Trajectory} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                              & AO                & SR                & AO               & SR               \\ \midrule
  Fixed direction             & 0.175             & 0.144             & 0.845            & 0.897            \\
  Follow the real target      & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
  \label{table:direction}
\end{table}

%%%% 问题 2.3 %%%%
\textit{3. For the experiments, the authors should conduct the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.}

\textbf{Thanks for your advice and we have conducted the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.
The detailed analysis of new added experiment is added in Section IV.D of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

\uline{\textit{Ablation Study: One Branch Attack} To evaluate the impact of $p$ and $\delta$, we add the ablation study on only adding perturbations on the template images or the search regions. The result is shown in Table \ref{table:one_branch}. Experiment results shows that only adding the perturbation to one branch is not useful.
% 对比无目标攻击性能。
For the untargeted attack, only attacking the template/search branch leads to the AO of 0.510/0.714, while attacking both branches leads to the AO of 0.153, which is more effective.
% 有目标
For the targeted attack, only attacking the templat/search branch leads to the AO of 0.156/0.160, while attacking both branches leads to the AO of 0.840. Experimental results show that attacking two branches can achieve better results than attacking one branch.}

@@

\begin{table}[]
  \centering
  \caption{Attack performance when only use the template/search perturbation.}
  \label{table:one_branch}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
                & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\
                & AO                & SR                & AO               & SR               \\ \midrule
  Only Template & 0.510             & 0.567             & 0.156            & 0.106            \\
  Only Search   & 0.714             & 0.841             & 0.160            & 0.132            \\
  Both          & 0.153             & 0.123             & 0.840            & 0.890            \\
  \bottomrule
  \end{tabular}
\end{table}

%%%% 问题 2.4 %%%%
\textit{4. As reviewer 1 and reviewer 2 say, the perturbations added to template regions and research regions are not imperceptible, which may be helpful to misguide the tracker. The reviewer considers that adding a similar random pattern on the template and search regions to further illustrate the effectiveness of the proposed method.}

\textbf{To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions: the mean value and standard deviation is the same as the template/search image.
For your convenience in cross-checking, the new text is given as follows.
}

@@

% figure 8
\textbf{In Figure VIII, we have replaced ``Adversarial patches of different sizes.'' with}
\uline{``Influence of the Adversarial Patch Size. In our experiment, we produce three different sizes of the adversarial patch, namely, 64-by-64, 32-by-32 and 16-by-16 to test the efficiency of their attacks. We evaluate the AO score of SiamFC++ on the perturbed GOT-Val dataset.''}
\textbf{in Section IV.D of the revised manuscript.}

\textit{4. I suggest adding the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion.}

\textbf{Thanks for the good commenet. As suggested, we have added the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion. For your convenience in cross-checking, the new text is given as follows.}

\uline{
Compared with other attack methods, our method has two key advantages. First,
  % 通用的，也就是不需要进行网络推断或者梯度计算，因此使得可以在不消耗计算资源的同时执行攻击成为可能。
because our video-agnostic feature, we are fast, no need to network interferes or gradient calculation, making it possible to attack a real-world online-tracking system when we can not get access to the limited computational resources.
Second, the proposed perturbations show good transferability to other anchor free or anchor based trackers. 
  %(1) Physical attack. We are the digital attack, which means ... Physical attack is ... The advantage of it is ... Our work assumes a threat model in which the adversary can feed data directly into the machine learning classifier. This is not always the case for systems operating in the physical world, for example those which are using signals from cameras and other sensors as input.
  % 这不就是 ICCV2019 的工作吗？它们也通用？好像是。EOT是通用的吗？
The main limitation of our work is the values of our universal perturbations are not as small as other non-universal perturbations due to the task difficulty.
% Future work:
  % (1) We need to do the physical attack.
  % (2) We need to be imperceptible.
  % 使用同一个扰动同时攻击多个视觉任务，包括图像分类，检测，视频目标跟踪和分割。
  In future work, we expect that it will be possible to demonstrate the existence of a single perturbation to attack multi vision tasks, including image classification, object detection and video object tracking/segementation.
  % 以更小的扰动取得更高的攻击效果。（呼应缺点之：扰动大）
  % Use more imperceptible perturbations to achieve high attack performance.
  % 本文所提出的对抗性信息被添加在数字图像上，从而影响跟踪器的跟踪效果。然而所提出的对抗性信息难以用于执行孪生跟踪器的物理攻击，即将对抗扰动打印出来添加到物理世界的真实目标上，从而影响孪生跟踪系统的性能。因为对抗扰动的打印过程可能改变扰动的值，且相机传感器可能无法感知较小的扰动。可能的解决方案是借助EOT生成针对相机距离和角度具有鲁棒性的物理扰动，使得在各种成像条件下，跟踪系统都无法对带有对抗性信息的真实目标进行正确跟踪。
  % 通过 *** 方式（比如，借助 *** 信息）实现物理攻击。
  % 防御？
}

@@

\textit{5. Some of the experiments require more explanations. For example, transferability has been investigated by different backbones \& architectures. It's needed to mention these experiments are with/without the training phase or not.}

\textbf{Thanks for the good comment. These experiments are without the training phase. These experiments do not need the training phase and we have clarified this in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

\uline{In this sub-section, we analyze the transferability of the proposed attack method. Specifically, the perterbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to other tracking networks including SiamFC++\_ShuffleNet, SiamFC++\_\\AlexNet, SiamPRN and SiamRPN++.}

@@

\textit{6. In experiments, I suggest considering two scenarios of different directions and trajectories.}

\textbf{Thanks for the good comment. As suggest, we consider an alternative way to generate the \textit{fake trajectory} without the use of the ground truth boxes. Specifically, the attacker forces the tracker to follow a fixed direction. We illustrate this with 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
% 介绍在什么数据集上做的实验，用的什么评价指标。
The attack performance is evaluated according to AO/SR on GOT-Val.
The detailed analysis of new added experiment is added in Section IV.D of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
写response

@@

@@

In this paper, we propose a video-agnostic targeted attack method for Siamese trackers. 
We aim to attack the tracker by adding a perturbation to the template image and adding a \textit{fake target}, \ie, a small adversarial patch, into the search image adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations.
Experiments on several popular datasets show that our method can effectively fool the Siamese trackers in a targeted attack manner.

By studying the attack method of Siamese trackers, we argue that the disadvantage of Siamese trackers is that template matching-based tracking mechanism is vulnerable to attacks, i.e., if both the template and the search image are perturbed at the same time, then the tracking algorithm can easily be misled.
The implication for improving the tracking robustness is to make the tracker aware of the semantic information of the target being tracked, rather than relying on templates alone, so that the semantic information can be relied on to ensure tracking robustness.

>>>>

\uline{In this sub-section, we analyze the transferability of the proposed attack method. Specifically, the perterbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to other tracking networks including SiamFC++\_ShuffleNet, SiamFC++\_AlexNet, SiamPRN and SiamRPN++.}

@@

\uline{Compared with other attack methods, our method has two key advantages. First, because our video-agnostic feature, we are fast, no need to network interferes or gradient calculation, making it possible to attack a real-world online-tracking system when we can not get access to the limited computational resources. Second, the proposed perturbations show good transferability to other anchor free or anchor based trackers. The main limitation of our work is the values of our universal perturbations are not as small as other non-universal perturbations due to the task difficulty.}

@@

In this paper, we propose a video-agnostic targeted attack method for Siamese trackers. 
We aim to attack the tracker by adding a perturbation to the template image and adding a \textit{fake target}, \ie, a small adversarial patch, into the search image adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations.
Experiments on several popular datasets show that our method can effectively fool the Siamese trackers in a targeted attack manner.
\uline{In future work, we expect that it will be possible to demonstrate the existence of a single perturbation to attack multi vision tasks, including image classification, object detection and video object tracking/segementation.}
% By studying the attack method of Siamese trackers, we argue that the disadvantage of Siamese trackers is that template matching-based tracking mechanism is vulnerable to attacks, i.e., if both the template and the search image are perturbed at the same time, then the tracking algorithm can easily be misled.
% The implication for improving the tracking robustness is to make the tracker aware of the semantic information of the target being tracked, rather than relying on templates alone, so that the semantic information can be relied on to ensure tracking robustness.
